Consumption and resistance across states and HRRs

### 2017-03-27 chronic-conditions/chronic-condition-drivers.Rmd
sex difference plots

I'll use the Medicare 2011 data with normal filters (age 65 or above, only beneficiaries on Medicare for 12 months of the year).

@@

```{r load_data}
denom = read_tsv('../bene_2011.tsv') %>%
  filter(age >= 65) %>%
  mutate(is_female=sex=='female') %>%
  select(bene_id, age, is_female)
chronic_conditions = read_tsv('cc_2011.tsv') %>%
  rename(bene_id=BENE_ID) %>%
  select(-STRCTFLG) %>%
  mutate_at(vars(AMI:HYPOTH), function(x) x==3)
usage = read_tsv('../pde_2011.tsv') %>%
  count(bene_id) %>% rename(n_claims=n)

>>>>

I'll use the Medicare 2011 data with normal filters (age 65 or above, only beneficiaries on Medicare for 12 months of the year). I'll run separate analyses on those under 65.

@@

```{r load_data}
all_denom = read_tsv('../bene_2011.tsv') %>%
  filter(age >= 65) %>%
  mutate(is_female=sex=='female') %>%
  select(bene_id, age, is_female)
chronic_conditions = read_tsv('cc_2011.tsv') %>%
  rename(bene_id=BENE_ID) %>%
  select(-STRCTFLG) %>%
  mutate_at(vars(AMI:HYPOTH), function(x) x==3)
usage = read_tsv('../pde_2011.tsv') %>%
  count(bene_id) %>% rename(n_claims=n)

### 2017-03-27 drug-drug-correlations/drug-drug.Rmd
sex difference plots

Consider two dichotomous variables $X$ and $Y$. Each joint observation ($x_i$, $y_i$) can be one of $(0, 0)$, $(0, 1)$, $(1, 0)$, or $(1, 1)$. The tetrachoric correlation finds a correlation $\rho$ by finding the "cutpoints" $tau_X$ and $tau_Y$ such that the bivariate standard normal distribution with correlation $\rho$ has "quadrants" with masses that best match the relative frequencies of the joint observations. For example, the "lower-left" quadrant has mass

@@

@@

>>>>

Consider two dichotomous variables $X$ and $Y$. Each joint observation ($x_i$, $y_i$) can be one of $(0, 0)$, $(0, 1)$, $(1, 0)$, or $(1, 1)$. The tetrachoric correlation finds a correlation $\rho$ by finding the "cutpoints" $\tau_X$ and $\tau_Y$ such that the bivariate standard normal distribution with correlation $\rho$ has "quadrants" with masses that best match the relative frequencies of the joint observations. For example, the "lower-left" quadrant has mass

@@

Yonatan has a number of interpretations and guesses:

- Azithromycin and levofloxacin are used for pneumonia, and they will also go in that sequential order
- Cipro, Bactrim, and nitro are for UTIs and will proceed in that order
- Keflex/Bactrim is for skin and soft tissue infections
- Cipro and metro are simulatenous
- Levo and metro are simulatneous

We should be able to compare these to what's actually happening, which is a
statement about prescribing practice.

@@

There is probably a technically-superior way to do this: I measured consumption
as an on-off thing, and the polychoric only works well with a small number of
categories. I may be able to reduce the number of claims into a small number of
groups (e.g., 0, 1, 2--5, etc.). I wonder also if there is a "Poisson regression",
where you postulate that the Poisson means are correlated.

### 2017-03-27 inequality-resistance/inequality-resistance.Rmd
sex difference plots

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, dev=c('pdf', 'png'), 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
```

### 2017-03-27 sex-difference/sex-difference.Rmd
sex difference plots

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/',
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

@@

```{r}
plot_dat = usage %>%
  select(age, sex) %>%
  filter(sex %in% c('male', 'female')) %>%
  group_by(age) %>% count(sex) %>% ungroup() %>%
  spread(sex, n, fill=0L) %>%
  mutate(total=female+male, grand_total=sum(total),
         fraction_year=total/grand_total, fraction_female=female/total)

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

@@

```{r sex_by_age}
plot_dat = usage %>%
  select(age, sex) %>%
  filter(sex %in% c('male', 'female')) %>%
  group_by(age) %>% count(sex) %>% ungroup() %>%
  spread(sex, n, fill=0L) %>%
  mutate(total=female+male, grand_total=sum(total),
         fraction_year=total/grand_total, fraction_female=female/total)

### 2017-03-27 states/resistance/state-report.Rmd
sex difference plots

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, cache=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r setup}
library(broom)
library(pander)
library(assertr)

# swo> I removed Klebsiella because it's mostly in immune-compromised people
# and K. oxytoca because it's from neonatal septicemia?
gram_negs = c('Escherichia coli',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

# swo> State beneficiary information could be used as control variables
# in regressions
#state_bene = read_tsv('../../bene-consumption/state-bene-2011.tsv') %>%
  #filter(state %in% known_states)

# State-level consumption data
state_consumption = read_tsv('../bene-consumption/state_usage_2011.tsv') %>%
  filter(!is.na(state)) %>%
  right_join(consumption_groups, by=c('antibiotic'='drug')) %>%
  group_by(state, drug_group) %>%
  summarize_at(vars(cpkp, did), sum)

>>>>

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, cache=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(broom)
library(pander)
library(assertr)
```

```{r setup}
# swo> I removed Klebsiella because it's mostly in immune-compromised people
# and K. oxytoca because it's from neonatal septicemia?
gram_negs = c('Escherichia coli',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

# swo> State beneficiary information could be used as control variables
# in regressions
#state_bene = read_tsv('../../bene-consumption/state-bene-2011.tsv') %>%
  #filter(state %in% known_states)
```

```{r load_consumption_data}
bene = read_tsv('../../bene_2011.tsv') %>%
  left_join(hrr, by='zipcode')
pde = read_tsv('../../pde_2011.tsv') %>%
  select(bene_id, drug=antibiotic) %>%
  left_join(select(bene, bene_id, state, hrr), by='bene_id')

na20 = function(x) if_else(is.na(x), 0L, x)

state_denom = bene %>% count(state) %>% rename(n_bene=n)
state_consumption = pde %>%
  group_by(state, drug) %>%
  summarize(n_claims=n()) %>%
  ungroup() %>%
  left_join(state_denom, by='state')

hrr_denom = bene %>% count(hrr) %>% rename(n_bene=n)
hrr_consumption = pde %>%
  group_by(hrr, drug) %>%
  summarize(n_claims=n()) %>%
  ungroup() %>%
  left_join(hrr_denom, by='hrr')

# State-level consumption data
#state_consumption = read_tsv('../bene-consumption/state_usage_2011.tsv') %>%
  #filter(!is.na(state)) %>%
  #right_join(consumption_groups, by=c('antibiotic'='drug')) %>%
  #group_by(state, drug_group) %>%
  #summarize_at(vars(cpkp, did), sum)
